Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-06-20 paper.tex
Do not speak about optimization.

The result of RRT is optimized in two steps (see~\cite{dalibard09} for details):
\begin{enumerate}
\item the path is extended in order to move the final posture closer to the rest posture,
\item the path is optimized by random short-cuts.
\end{enumerate}

Extension 1 presents a video of this motion.

@@

We have run this set of motion planning problems 20 times. The results are compiled in Table~\ref{table:reaching}. We can notice that optimization dominates the total time of computation. This suggests that improvement can be easily achieved by using numerical optimization techniques. This is on-going work.
\begin{table}
\begin{tabular}{lrrrr}
& min & max & average & average \\ 
&&&& per problem \\
number of nodes & 43.00 & 481.00 & 102.70 \\
goal generation time \hspace {1.cm} & 1.00 & 1.56 & 1.22\\
planning time& 67.36 & 376.84 & 134.28 & 44.76\\
optimization time & 204.22 & 671.26 & 521.47 & 173.82 \\
total times & 468.23 & 864.68 & 656.97 &
\end{tabular}
\caption {Experimental results on 20 runs: 3 motion planning problems and 2 goal generations. Times are expressed in seconds.}
\label{table:reaching}
\end{table}

>>>>

Extension 1 presents a video of this motion after an optimization step.

@@

We have run this set of motion planning problems 20 times. The results are compiled in Table~\ref{table:reaching}.
\begin{table}
\begin{tabular}{lrrrr}
& min & max & average & average \\ 
&&&& per problem \\
number of nodes & 43.00 & 481.00 & 102.70 \\
goal generation time \hspace {1.cm} & 1.00 & 1.56 & 1.22\\
planning time& 67.36 & 376.84 & 134.28 & 44.76\\
\end{tabular}
\caption {Experimental results on 20 runs: 3 motion planning problems and 2 goal generations. Times are expressed in seconds.}
\label{table:reaching}
\end{table}
